### 2018-09-05 doc/plos/text/manuscript.tex
discuss things

MASE is reasonably subject to being greater than one, indicating that the
nowcast under consideration performed \textit{worse} than the ``naive''
nowcast. This should be unsurprising, if not expected, given that the naive
oracle incorporates information which is not available at runtime.

That the nowcast is more accurate than its individual inputs should hold in
general as the outputs of sensor fusion should, on average, have smaller error
than the inputs. However, this may not hold in all cases due to overfitting or
violations of the assumptions of linearity and normality.

@@

TODO(curse of dimensionality and regularization)

TODO(ablation: overfitting, assumptions, time-variable relationships)

TODO(more discussion)

>>>>

We compared nowcasts with two baselines; a naive oracle, which reports
finalized wILI on the previous week, and a simple method, which reports the
median sensor reading on a given week. At high geographic resolution (i.e.
states, territories, and cities), we find that sensor fusion nowcasts are
cumulatively approximately on par with naive oracle nowcasts and somewhat
better than simple nowcasts. At lower geographic resolution (i.e. regionally
and nationally), sensor fusion nowcasts strongly and uniformly outperform both
baselines.

MASE---error of sensor fusion nowcasts relative to error of the naive
oracle---is frequently greater than one in small geographic units, indicating
that the nowcast under consideration performed \textit{worse} than the
so-called ``naive'' nowcast. This result is not entirely unexpected, given that
the naive oracle incorporates latent information (namely, finalized ILI) which
is unavailable to operational nowcasts at runtime.

That the nowcast is more accurate than its individual inputs (i.e. ``sensors'')
should hold in general as the outputs of sensor fusion should, on average, have
smaller error than the inputs. Overfitting or violations of the assumptions of
linearity and normality may cause deviations from this expectation.

We observe such deviations at least twice. First, for the set of five states,
territories, and cities within HHS region two (``HHS2''), we find that the
geometric mean of RelMAE---error of sensor fusion nowcasts relative to error of
the simple baseline---is greater than one, meaning that the baseline
outperformed the nowcast in these locations. Second, we find that removal of
certain sensors (``ablation'' and ``abscission'' experiments) causes the
accuracy of the nowcast to improve. In both of these situations, less data is
better than more data, against expectation.

Our estimate of the covariance of sensor ``noise'' (residuals w.r.t. ground
truth) $R$ is necessarily imperfect. Adding additional sensors exponentially
increases the dimension of the problem without adding new observations---the
curse of dimensionality. With 367 sensor-location pairs, $R$ has shape $367
\times 376$; yet in the best case we only have a few hundred observations from
which to estimate this covariance---often much fewer. Our only recourse is
aggressive regularization at the expense of covariance accuracy, and therefore
nowcast accuracy.

Linearity between sensors and ground truth and normality of sensor noise are
each merely assumed. Violations of these assumptions are neither tested for nor
acted upon. The sensor fitting procedure simply centers and scales raw data to
fit ground truth in a least-squares sense. It is possible, if not likely, that
some sensors are nonlinear w.r.t. ground truth or have non-normal residuals (or
both). When this is the case, nowcasts will be less accurate; sensor fusion, at
least as formulated above, operates in terms of linear combinations of
multivariate normal distributions.

Additionally, we make the implicit assumption that the relationship between
each sensor and ground truth is constant over time. That is, we assume that the
bias and variance of residuals are fixed. (In contrast, we explicitly account
for a time-varying relationship between raw data and ground truth in the sensor
fitting procedure.) However, this is almost certainly violated in some
situations; for example, digital surveillance is disproportionately affected
during periods of heightened traditional and social media coverage of
outbreaks.

@@

TODO: merits and drawbacks of sensor fusion
